\package{}: an \R{} package for implemetation of the ITHIM model

### 2016-09-13 manuscript/manuscript.tex
Bugs from merge ironed out.

\begin{methods}
\section{Methods}
\begin{itemize}
\item The coefficient of variation was fixed at ??? for all models.
  Earlier ITHIM models estimated this as a function of total active
  tranpsort time to model the decrease in variance of active transport
  time that occurs for increasing means, i.e., fitter communities have
  less variance in active transport time.
\item The mean non-travel activity for the referent group was modeled
  as a variable.  The relative means across age-sex strata were fixed,
  and estimated using ATUS.
\item The national DALYs were stimated using the attributable fraction
  provided by the comparitive risk assesment.  The estimates for
  disease burned came from WHO and their GBD study.
\item Not all of the regions had the same sample size.  In fact a few
  of the regions have relativel low sample size.  Maybe we should put
  confidence intervals on our estimates.
\end{itemize}

@@

\section{Regional Example}
>>>>>>> 72bfec401397d734de4e6e2096ea97c4bd3437ce
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur
adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore
magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
ullamco laboris nisi ut aliquip ex ea commodo consequat.

@@

\end{methods}
\section*{Acknowledgment}

>>>>

\begin{methods}

\section{Methods}

\begin{itemize}
\item The coefficient of variation was fixed at ??? for all models.
  Earlier ITHIM models estimated this as a function of total active
  tranpsort time to model the decrease in variance of active transport
  time that occurs for increasing means, i.e., fitter communities have
  less variance in active transport time.
\item The mean non-travel activity for the referent group was modeled
  as a variable.  The relative means across age-sex strata were fixed,
  and estimated using ATUS.
\item The national DALYs were stimated using the attributable fraction
  provided by the comparitive risk assesment.  The estimates for
  disease burned came from WHO and their GBD study.
\item Not all of the regions had the same sample size.  In fact a few
  of the regions have relativel low sample size.  Maybe we should put
  confidence intervals on our estimates.
\end{itemize}

@@

\section{Regional Example}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut
aliquip ex ea commodo consequat. Duis aute irure dolor in
reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum
dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
occaecat cupidatat non proident, sunt in culpa qui officia deserunt
mollit anim id est laborum. Lorem ipsum dolor sit amet, consectetur
adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore
magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
ullamco laboris nisi ut aliquip ex ea commodo consequat.

@@
